Client-Side Indexes for Fast Full-Text Searching

### 2014-12-08 paper/paper.tex
introduction of indexeddb

>>>>

Indexed Database (IndexedDB) is a Javascript API that was a Proposed Recommendation to the W3C on November 20th 2014~\cite{w3c} and is supported by most modern browsers on the desktop and phone, such as newer versions of Chrome, Firefox, Internet Exploror, Opera, and Safari. For our implementation, we focused our testing and demos on the Chrome browser as it is currently the most widely used.
On Chrome browsers, IndexedDB interfaces with a key-value store named LevelDB built at Google in C++ and inspired by BigTable. In LevelDB, keys and values are arbitrary byte arrays and data is stored in sorted order by key. It supports batch writing, put and get commands using the key, and forward and backward iteration over keys.

The IndexedDB API supports transactions that rely on strict two-phase locking, so that read-only transactions can run concurrently but read-write transactions lock the specified object stores (similar to tables in a relational data store) for the entire duration of the transaction.
Almost all transactions in IndexedDB are asynchronous, meaning that one must request for a database operation, such as a put or a get, to happen and then pass a callback function. Then a notification via a DOM event is triggered when the operation actually completes, and the type of event returned tells whether the operation succeeded or failed.
